% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{hyperref}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\topmargin=-0.5in  % start text higher on the page
\textheight=700pt % add more space to page

\begin{document}
\name{FELIX CHAPMAN \vspace{0.2in}}

\address{
\begin{minipage}[t]{0.25\textwidth}
London \\
United Kingdom
\end{minipage}
\begin{minipage}[t]{0.25\textwidth}
+44 7977 871939 \\
\href{https://ael.red/}{https://ael.red/} \\
\href{mailto:aelred717@gmail.com}{aelred717@gmail.com} \\
\href{https://www.github.com/aelred}{github.com/aelred}
\vspace{0.1in} \\
\end{minipage}
}

\begin{resume}

\section{PERSONAL STATEMENT}

A motivated, skilled software developer with experience in backend development primarily in Java, Python and Rust, looking to resume my career after a break travelling and volunteering.

\section{EXPERIENCE}

\normalsize{\section{2015 - 2018}}
{\bf Vaticle} (formerly Grakn Labs, \href{https://typedb.com/}{https://typedb.com/}) \\
Core Developer
\begin{itemize}

\item
Created TypeQL (formerly Graql, \href{https://typedb.com/docs/typeql/2.x/overview.html}{https://typedb.com/docs/typeql/2.x/overview.html}), a declarative pattern-based query language that operates on the TypeDB (formerly Grakn) graph database, implemented in Java, using Tinkerpop and ANTLR.

\item
Achieved remote query execution using protocol buffers and gRPC to stream results over HTTP. I implemented remote clients in Java, Python and Haskell.

\item
Improved performance of query execution in Moogi - a movie semantic search engine used to demonstrate our software stack.

\item
Supported loading database schemas into the graph by building a parser for CTM (compact topic map) files.

\item
Helped implement company processes such as code reviews and automated testing using Travis CI and Jenkins.

\end{itemize}

\normalsize{\section{2014}}
{\bf University of Southampton} \\
Internship, PLEASED project

\begin{itemize}

\item
Performed classification on signals from plants in response to stimulus.

\item
Developed Python scripts using scipy and scikit-learn to perform machine learning techniques such as linear discriminant analysis and source separation.

\end{itemize}

\normalsize{\section{2011}}
{\bf Mrs. Helsby} \\
Database administrator and application developer \\
\begin{itemize}
\item Developed a database to manage the availability and pricing of two houses
\item Developed in Microsoft Access using SQL statements and VB scripts
\item Created a GUI that was easy for the end-user to understand and use
\end{itemize}

\normalsize{\section{2007}}
{\bf C\&J Clark International} \\
Work experience student, IT \\
\begin{itemize}
\item One week school-arranged work experience
\item Basic IT skills: entering data, working with people across time zones
\item Team-based activities
\end{itemize}

\section{VOLUNTEERING}

\normalsize{\section{2018}}
{\bf Montana Youth Hostel, Bergen} (\href{https://www.montana.no/}{https://www.montana.no/}) \\
Social Volunteer \\
\begin{itemize}
\item
Guided guests on day hikes in the surrounding mountains.
\item
Organised activities and helped the staff.
\end{itemize}

\section{PROJECTS}

\normalsize{\section{Tetris}}
Project to learn Rust. Used SDL and compiled into Wasm. (\href{https://tetris.ael.red/}{https://tetris.ael.red/})

\normalsize{\section{Starling}}
A functional programming language implemented in Python. (\href{https://github.com/aelred/starling}{https://github.com/aelred/starling})

\section{EDUCATION}
\normalsize{\section{2011 - 2015}}
{\bf University of Southampton} \\
MEng Computer Science with First Class Honours \\
\normalsize{\section{2009 - 2011}}
{\bf Strode College, Street}

{\bf A Levels} \\
Computing (A*) \\
Mathematics (A*) \\
Physics (A) \\
Music (D)

{\bf Additional achievements} \\
College Ensemble \\
Jazz Group \\
Managing Personal Finance Award

\normalsize{\section{2004 - 2009}}
{\bf St. Dunstan's Community School, Glastonbury}

{\bf GCSEs} \\
Mathematics (A*) \\
Science (A*) \\
Additional Science (A) \\
English Language (A) \\
English Literature (A) \\
French (A*) \\
History (A) \\
Music (A) \\
Art and Design (C)

\section{SKILLS}

\normalsize{\section{Programming languages}}
Proficient in Java, Scala, Python and Rust. \\
Experience with JavaScript, TypeScript, C\#, C, Kotlin, Haskell and Visual Basic.

\normalsize{\section{Technologies}}
gRPC, protocol buffers, Git, ANTLR, SDL, Tinkerpop, Gradle, Maven, CircleCI, Travis CI, Jenkins, FHIR, Terraform, Kubernetes

\normalsize{\section{Computer skills}}
\begin{itemize}
\item Experience using Windows, Linux and macOS
\item Experience with Microsoft Office and Google Workspace
\end{itemize}

\normalsize{\section{Other skills}}
\begin{itemize}
\item Understanding and interest in machine learning
\item Good understanding and application of mathematics
\end{itemize}

\section{HONOURS}
\begin{itemize}
\item At the University of Southampton, awarded a Zepler scholarship in
Electronics and Computer Science in first and second year for outstanding
achievement.
\end{itemize}

\section{HOBBIES}
\begin{itemize}
\item Playing piano (grade 8), particularly classical music and jazz
\item Playing and developing videogames
\item Solving programming problems on sites such as
\href{https://projecteuler.net/}{projecteuler.net}
\end{itemize}

\end{resume}

\end{document}

