\documentclass[a4paper, margin=0.3in]{letter}
\usepackage{hyperref}

\signature{Felix Chapman}

\address{
Felix Chapman \\
The White Cottage \\
Burnetts Lane \\   
Baltonsborough \\   
Glastonbury \\ 
United Kingdom \\
BA6 8RD \\ \\
Home:	01458 850191 \\
Mobile:	07875983083 \\
\href{mailto:aelred717@gmail.com}{aelred717@gmail.com}
}

\longindentation=0pt

\begin{document}

\begin{letter}{}

\opening{Dear Sir or Madam,}

I am writing to apply for the Summer Student Programme at CERN and am available for any of the possible dates. I am a B.Sc. Computer Science student in my second year at Southampton University and have achieved marks in the top 10\% last year, with comparable results in my second year, having previously gained an A* at A-Level (GCE Advanced Level, age 18) in computing.

I would like to be considered for this year's internship and am particularly interested in the listed areas of cloud computing and automation software. As well as my skills and active interest in computer science, I have a strong understanding of maths and physics, receiving an A* and A respectively at A-Level. During my course, the relevant subjects I have studied include distributed computing, communications and networks, database systems and software engineering. I enjoy following recent advances in science and technology, such as progress in 3D printing and augmented reality technologies. 

I took French at GCSE level (age 16) and achieved an A*. I am considered to be fair, approachable and friendly and I work well individually and in a group; I'm often picked as the leader for group work, and recently I was chosen to organize and arrange the meetings for a group software engineering project this year. Outside university, I enjoy playing the piano and playing video games.

I would be very interested to learn more about cloud and distributed computing, as well as to further my knowledge of physics. The prospect of working at CERN is very exciting for me as it will give me real and relevant experience with modern, state-of-the-art research equipment and technologies. I would be very proud to have internship experience with such a reputable organisation.

Thank you very much for considering my application and CV and I hope to hear from you.

\closing{Yours faithfully,}

\end{letter}

\end{document}